---
title: "Replication of Enos Paper"
author: "Sean Hughes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Install Required Packages
rm(list = ls())

library(ri)
library(RItools)
library(car)
library(xtable)
library(effects)
library(RColorBrewer)
library(gt)
library(knitr)
library(dplyr)
library(data.table)


# Set for non-scientific notaion output
options(scipen = 999)

# Load data

dat.all = read.csv('./csvData/pnas_data.csv')
dat.t1 = read.csv('./csvData/t1_data.csv')
dat.all.prime = read.csv('./csvData/prime_data.csv')

# Data loading for faces graphic
conf.dat = read.csv('./csvData/confederate_face_data.csv')
hisp.dat = read.csv('./csvData/hispanic_face_data.csv')
white.dat = read.csv('./csvData/white_face_data.csv')

```

## Abstract

I use the Harvard Dataverse data to replicate figures from the paper ["Causal Effect of Intergroup Contact on Exclusionary Attitudes"](https://scholar.harvard.edu/files/renos/files/enostrains.pdf).

```{r echo = FALSE, warning=FALSE, message=FALSE, include = FALSE}

### Main results

# Initialize variables for inference.

repeats <- c("numberim", "Remain", "Englishlan")
x.names <- paste(repeats, ".x", sep = "")
y.names <- paste(repeats, ".y", sep = "")
covariates <- c("line.x")
## Treated first
# Initiatize a blank df
# with 8 columns.
final.mat <- matrix(nrow = 0, ncol = 8)
# Loop through "all" and "no.car".
subsets <- c("all", "no.car")
for (subset in subsets) {
  # Make a new matrix with 8 columns and
  # three rows, one for each question.
  out.mat <- matrix(nrow = length(repeats), ncol = 8)
  # If we're looking at all of the data,
  # subset the data to all the data. If
  # we want just the no.car data, filter to include
  # only people with habits equal to NA, 2, or 3
  if (subset == "all") {
    dat.subset <- dat.all
  }
  if (subset == "no.car") {
    dat.subset <- dat.all[dat.all$habits != 1, ]
  }
  z.variable <- "treatment"
  # Loop through survey questions 1, 2, and 3. Manually rescale answers to
  # questions to lie between 0 and 1 (i.e., 0, .25, .5, etc.). Then calculate the difference
  # between the x and y answers [this may be pre- and post-treatment].
  for (j in 1:length(repeats)) {
    dat.subset$x.new <- (as.numeric(dat.subset[, x.names[j]]) - 1) / 4 ## rescale x to 0-1
    dat.subset$y.new <- (as.numeric(dat.subset[, y.names[j]]) - 1) / 4 ## rescale y to 0-1
    dat.subset$Y <- dat.subset$y.new - dat.subset$x.new
    # Remove the NA values.
    dat.use <- dat.subset[is.na(dat.subset$Y) == F, ]
    # Find the sd and means of the new data.
    # x.sd is the sd of the pre-treatment results.
    # x.mean is the mean of the pre-treatment results.
    # y.mean is the mean of the post-treatment results.
    # y.treat is the mean of the post-treatment responses for treated individuals.
    x.sd <- sd(dat.use$x.new, na.rm = T)
    x.mean <- mean(dat.use$x.new, na.rm = T)
    y.mean <- mean(dat.use$y.new, na.rm = T)
    y.treat <- mean(dat.use$y.new[dat.use$treatment == 1], na.rm = T)
    # Make a table with the number of treated individuals at each station.
    station.treatment.table <- table(dat.use$station, dat.use[, z.variable])
    # Identify the stations with no controls or no treatments,
    # and exlude those from the usable data.
    no.control.stations <- names(which(station.treatment.table[, 1] == 0))
    no.treatment.stations <- names(which(station.treatment.table[, 2] == 0))
    dat.use <- dat.use[!dat.use$station %in% c(no.control.stations, no.treatment.stations), ]
    # Make the stations and treated units factors.
    dat.use$station <- factor(dat.use$station)
    dat.use$treated_unit <- factor(dat.use$treated_unit)
    # This selects only the dat.use$line.x observations.
    Xs <- data.matrix(dat.use[, covariates])
    # Generates a permutation matrix for randomized blocks (?)
    # by station and randomized clusters by treatment unit.
    perms <- genperms(Z = dat.use[, z.variable], blockvar = dat.use$station, clustvar = dat.use$treated_unit)
    probs <- genprobexact(Z = dat.use[, z.variable], blockvar = dat.use$station, clustvar = dat.use$treated_unit)
    # Generate estimated average treatment effects,
    # hypothesized potential outcomes, randomized
    # distribution of estimated ATEs, and estimated
    # ATE distribution.
    ate <- estate(Y = dat.use$Y, Z = dat.use[, z.variable], X = Xs, prob = probs)
    Ys <- genouts(Y = dat.use$Y, Z = dat.use[, z.variable], ate = 0)
    distout <- gendist(Ys, perms, prob = probs)
    disp <- dispdist(distout, ate = ate, display.plot = F)
    # Save everything into a matrix and
    # attach by rows to a final matrix.
    out.mat[j, 1] <- repeats[j]
    out.mat[j, 2] <- subset
    out.mat[j, 3] <- nrow(dat.use)
    out.mat[j, 4] <- ate
    out.mat[j, 5] <- disp$greater.p.value
    out.mat[j, 6] <- disp$lesser.p.value
    out.mat[j, 7] <- x.sd
    out.mat[j, 8] <- x.mean
  }
  final.mat <- rbind(final.mat, out.mat)
}
# Add column names and save for the final graph.
final.mat <- as.data.frame(final.mat)
colnames(final.mat) <- c("variable", "subset", "N", "ate", "greater.p.value", "lesser.p.value", "x.sd", "x.mean")
# print(final.mat)
final.mat.main <- final.mat

```


```{r echo = FALSE, warning=FALSE, message=FALSE, cache = TRUE, include = FALSE}
### Subset inference
var.names <- c("Number of immigrants be increased?", "Children of undocumented be allowed to stay?", "English as official language?")
# Dose response estimates comparison. Original code
# reuses the final.mat variable and creates new subset names.
final.mat <- matrix(nrow = 0, ncol = 8)
subsets <- c("ta", "tb")
# Iterate through ta and tb.
for (subset in subsets) {
  # Initialize an empty matrix (for output) and
  # a Z variable for later use.
  out.mat <- matrix(nrow = length(repeats), ncol = 8)
  z.variable <- "treatment"
  # Subset the data based on whether the observation
  # is in ta or tb.
  if (subset == "ta") {
    dat.subset <- dat.all[dat.all$t.time %in% c("t2a", "t4a"), ]
  }
  if (subset == "tb") {
    dat.subset <- dat.all[dat.all$t.time %in% c("t2b", "t4b"), ]
  }
  # Go through the same set of procedures as above. Rescale from 0
  # to 1, find the sd and means, construct the genperms and other
  # models, etc.
  for (j in 1:length(repeats)) {
    dat.subset$x.new <- (as.numeric(dat.subset[, x.names[j]]) - 1) / 4 ## rescale x to 0-1
    dat.subset$y.new <- (as.numeric(dat.subset[, y.names[j]]) - 1) / 4 ## rescale y to 0-1
    dat.subset$Y <- dat.subset$y.new - dat.subset$x.new
    dat.use <- dat.subset[is.na(dat.subset$Y) == F, ]
    x.sd <- sd(dat.use$x.new, na.rm = T)
    x.mean <- mean(dat.use$x.new, na.rm = T)
    station.treatment.table <- table(dat.use$station, dat.use[, z.variable])
    no.control.stations <- names(which(station.treatment.table[, 1] == 0))
    no.treatment.stations <- names(which(station.treatment.table[, 2] == 0))
    dat.use <- dat.use[!dat.use$station %in% c(no.control.stations, no.treatment.stations), ]
    dat.use$station <- factor(dat.use$station)
    dat.use$treated_unit <- factor(dat.use$treated_unit)
    Xs <- data.matrix(dat.use[, covariates])
    perms <- genperms(Z = dat.use[, z.variable], blockvar = dat.use$station, clustvar = dat.use$treated_unit)
    probs <- genprobexact(Z = dat.use[, z.variable], blockvar = dat.use$station, clustvar = dat.use$treated_unit)
    ate <- estate(Y = dat.use$Y, Z = dat.use[, z.variable], X = Xs, prob = probs)
    Ys <- genouts(Y = dat.use$Y, Z = dat.use[, z.variable], ate = ate)
    distout <- gendist(Ys, perms, prob = probs)
    disp <- dispdist(distout, ate = ate, display.plot = F)
    # Record the results in an output matrix and
    # bind it into a final df.
    out.mat[j, 1] <- repeats[j]
    out.mat[j, 2] <- subset
    out.mat[j, 3] <- nrow(dat.use)
    out.mat[j, 4] <- ate
    out.mat[j, 5] <- x.mean
    out.mat[j, 6] <- x.sd
    out.mat[j, 7] <- disp$quantile[1]
    out.mat[j, 8] <- disp$quantile[2]
  }
  final.mat <- rbind(final.mat, out.mat)
}
final.mat <- as.data.frame(final.mat)
colnames(final.mat) <- c("variable", "subset", "N", "ate", "x.mean", "x.sd", "quantile.lower", "quantile.upper")
# print(final.mat)
# Save for the final graph
final.mat.dose <- final.mat
## Compare ideology
final.mat <- matrix(nrow = 0, ncol = 8)
subsets <- c("liberals.only", "moderates.only", "conservatives.only")
for (subset in subsets) {
  # As above, subset the data by code (three levels)
  # based on liberal, conservative, or moderate responses.
  out.mat <- matrix(nrow = length(repeats), ncol = 8)
  if (subset == "liberals.only") {
    dat.subset <- dat.all[dat.all$ideology.x %in% c(1, 2), ]
  }
  if (subset == "conservatives.only") {
    dat.subset <- dat.all[dat.all$ideology.x %in% c(4, 5), ]
  }
  if (subset == "moderates.only") {
    dat.subset <- dat.all[dat.all$ideology.x == 3, ]
  }
  z.variable <- "treatment"
  # As above, rescale, find means, construct models.
  for (j in 1:length(repeats)) {
    dat.subset$x.new <- (as.numeric(dat.subset[, x.names[j]]) - 1) / 4 ## rescale x to 0-1
    dat.subset$y.new <- (as.numeric(dat.subset[, y.names[j]]) - 1) / 4 ## rescale y to 0-1
    dat.subset$Y <- dat.subset$y.new - dat.subset$x.new
    x.sd <- sd(dat.use$x.new, na.rm = T)
    x.mean <- mean(dat.use$x.new, na.rm = T)
    station.treatment.table <- table(dat.use$station, dat.use[, z.variable])
    no.control.stations <- names(which(station.treatment.table[, 1] == 0))
    no.treatment.stations <- names(which(station.treatment.table[, 2] == 0))
    dat.use <- dat.use[!dat.use$station %in% c(no.control.stations, no.treatment.stations), ]
    dat.use$station <- factor(dat.use$station)
    dat.use$treated_unit <- factor(dat.use$treated_unit)
    Xs <- data.matrix(dat.use[, covariates])
    perms <- genperms(Z = dat.use[, z.variable], blockvar = dat.use$station, clustvar = dat.use$treated_unit)
    probs <- genprobexact(Z = dat.use[, z.variable], blockvar = dat.use$station, clustvar = dat.use$treated_unit)
    ate <- estate(Y = dat.use$Y, Z = dat.use[, z.variable], X = Xs, prob = probs)
    Ys <- genouts(Y = dat.use$Y, Z = dat.use[, z.variable], ate = ate)
    distout <- gendist(Ys, perms, prob = probs)
    disp <- dispdist(distout, ate = ate, display.plot = F)
    # Add to the final matrix.
    out.mat[j, 1] <- repeats[j]
    out.mat[j, 2] <- subset
    out.mat[j, 3] <- nrow(dat.use)
    out.mat[j, 4] <- ate
    out.mat[j, 5] <- x.mean
    out.mat[j, 6] <- x.sd
    out.mat[j, 7] <- disp$quantile[1]
    out.mat[j, 8] <- disp$quantile[2]
  }
  final.mat <- rbind(final.mat, out.mat)
}
final.mat <- as.data.frame(final.mat)
colnames(final.mat) <- c("variable", "subset", "N", "ate", "x.mean", "x.sd", "quantile.lower", "quantile.upper")
# print(final.mat)
# Save for the final graph
final.mat.ideology <- final.mat
## Friends comparison
final.mat <- matrix(nrow = 0, ncol = 8)
subsets <- c("low.friends", "high.friends", "middle.friends")
for (subset in subsets) {
  out.mat <- matrix(nrow = length(repeats), ncol = 8)
  if (subset == "low.friends") {
    dat.subset <- dat.all[dat.all$Friends.x == 0, ]
  }
  if (subset == "high.friends") {
    dat.subset <- dat.all[dat.all$Friends.x >= 5, ]
  }
  if (subset == "middle.friends") {
    dat.subset <- dat.all[dat.all$Friends.x > 0 & dat.all$Friends.x < 5, ]
  }
  z.variable <- "treatment"
  for (j in 1:length(repeats)) {
    dat.subset$x.new <- (as.numeric(dat.subset[, x.names[j]]) - 1) / 4 ## rescale x to 0-1
    dat.subset$y.new <- (as.numeric(dat.subset[, y.names[j]]) - 1) / 4 ## rescale y to 0-1
    dat.subset$Y <- dat.subset$y.new - dat.subset$x.new
    dat.use <- dat.subset[is.na(dat.subset$Y) == F, ]
    x.sd <- sd(dat.use$x.new, na.rm = T)
    x.mean <- mean(dat.use$x.new, na.rm = T)
    station.treatment.table <- table(dat.use$station, dat.use[, z.variable])
    no.control.stations <- names(which(station.treatment.table[, 1] == 0))
    no.treatment.stations <- names(which(station.treatment.table[, 2] == 0))
    dat.use <- dat.use[!dat.use$station %in% c(no.control.stations, no.treatment.stations), ]
    dat.use$station <- factor(dat.use$station)
    dat.use$treated_unit <- factor(dat.use$treated_unit)
    Xs <- data.matrix(dat.use[, covariates])
    perms <- genperms(Z = dat.use[, z.variable], blockvar = dat.use$station, clustvar = dat.use$treated_unit)
    probs <- genprobexact(Z = dat.use[, z.variable], blockvar = dat.use$station, clustvar = dat.use$treated_unit)
    ate <- estate(Y = dat.use$Y, Z = dat.use[, z.variable], X = Xs, prob = probs)
    Ys <- genouts(Y = dat.use$Y, Z = dat.use[, z.variable], ate = ate)
    distout <- gendist(Ys, perms, prob = probs)
    disp <- dispdist(distout, ate = ate, display.plot = F)
    # Fill the final matrix.
    out.mat[j, 1] <- repeats[j]
    out.mat[j, 2] <- subset
    out.mat[j, 3] <- nrow(dat.use)
    out.mat[j, 4] <- ate
    out.mat[j, 5] <- x.mean
    out.mat[j, 6] <- x.sd
    out.mat[j, 7] <- disp$quantile[1]
    out.mat[j, 8] <- disp$quantile[2]
  }
  final.mat <- rbind(final.mat, out.mat)
}
final.mat <- as.data.frame(final.mat)
colnames(final.mat) <- c("variable", "subset", "N", "ate", "x.mean", "x.sd", "quantile.lower", "quantile.upper")
# Save for the final graph
final.mat.friends <- final.mat
## Income subsets
subsets <- c("low.income", "middle.income", "high.income")
final.mat <- matrix(nrow = 0, ncol = 8)
for (subset in subsets) {
  out.mat <- matrix(nrow = length(repeats), ncol = 8)
  if (subset == "low.income") {
    dat.subset <- dat.all[dat.all$income.new < 105000, ]
  }
  if (subset == "middle.income") {
    dat.subset <- dat.all[dat.all$income.new >= 105000 & dat.all$income.new <= 135000, ]
  }
  if (subset == "high.income") {
    dat.subset <- dat.all[dat.all$income.new > 135000, ]
  }
  z.variable <- "treatment"
  for (j in 1:length(repeats)) {
    dat.subset$x.new <- (as.numeric(dat.subset[, x.names[j]]) - 1) / 4 ## rescale x to 0-1
    dat.subset$y.new <- (as.numeric(dat.subset[, y.names[j]]) - 1) / 4 ## rescale y to 0-1
    dat.subset$Y <- dat.subset$y.new - dat.subset$x.new
    dat.use <- dat.subset[is.na(dat.subset$Y) == F, ]
    x.sd <- sd(dat.use$x.new, na.rm = T)
    x.mean <- mean(dat.use$x.new, na.rm = T)
    station.treatment.table <- table(dat.use$station, dat.use[, z.variable])
    no.control.stations <- names(which(station.treatment.table[, 1] == 0))
    no.treatment.stations <- names(which(station.treatment.table[, 2] == 0))
    dat.use <- dat.use[!dat.use$station %in% c(no.control.stations, no.treatment.stations), ]
    dat.use$station <- factor(dat.use$station)
    dat.use$treated_unit <- factor(dat.use$treated_unit)
    Xs <- data.matrix(dat.use[, covariates])
    perms <- genperms(Z = dat.use[, z.variable], blockvar = dat.use$station, clustvar = dat.use$treated_unit)
    probs <- genprobexact(Z = dat.use[, z.variable], blockvar = dat.use$station, clustvar = dat.use$treated_unit)
    ate <- estate(Y = dat.use$Y, Z = dat.use[, z.variable], X = Xs, prob = probs)
    Ys <- genouts(Y = dat.use$Y, Z = dat.use[, z.variable], ate = ate)
    distout <- gendist(Ys, perms, prob = probs)
    disp <- dispdist(distout, ate = ate, display.plot = F)
    # Fill matrix.
    out.mat[j, 1] <- repeats[j]
    out.mat[j, 2] <- subset
    out.mat[j, 3] <- nrow(dat.use)
    out.mat[j, 4] <- ate
    out.mat[j, 5] <- x.mean
    out.mat[j, 6] <- x.sd
    out.mat[j, 7] <- disp$quantile[1]
    out.mat[j, 8] <- disp$quantile[2]
  }
  final.mat <- rbind(final.mat, out.mat)
}
final.mat <- as.data.frame(final.mat)
colnames(final.mat) <- c("variable", "subset", "N", "ate", "x.mean", "x.sd", "quantile.lower", "quantile.upper")
# Save for the final table
final.mat.income <- final.mat
```


```{r echo = FALSE, warning=FALSE, message=FALSE, include = FALSE}
### Prime test
# Use randomization inference to look for changes
# in responses induced by experiment in subsets by covariates.
## Recodes
# Race
dat.all.prime$non.white <- ifelse(dat.all.prime$race_4 == 1, 1, 0)
dat.all.prime$non.white[is.na(dat.all.prime$non.white) == T] <- 0
# Residency
dat.all.prime$residency.new[dat.all.prime$residency == 1] <- 1
dat.all.prime$residency.new[dat.all.prime$residency == 2] <- 3.5
dat.all.prime$residency.new[dat.all.prime$residency == 3] <- 7.5
dat.all.prime$residency.new[dat.all.prime$residency == 4] <- 12.5
dat.all.prime$residency.new[dat.all.prime$residency == 5] <- mean(dat.all.prime$age, na.rm = T) - 15
dat.all.prime$residency.new[dat.all.prime$residency == 6] <- mean(dat.all.prime$age, na.rm = T)
# English language is reverse coded from other variables.
dat.all.prime$Englishlan.x <- recode(dat.all.prime$Englishlan.x, "5=1; 4=2; 3=3; 2=4; 1=5")
dat.all.prime$Englishlan.y <- recode(dat.all.prime$Englishlan.y, "5=1; 4=2; 2=4; 1=5")
# Gender
dat.all.prime$male <- ifelse(dat.all.prime$gender == 1, 1, 0)
## Inference
covariates <- c("line")
final.mat <- matrix(nrow = 0, ncol = 8)
subsets <- c("all.prime")
## Only complier and non-complier subsets [?]
for (subset in subsets) {
  out.mat <- matrix(nrow = length(repeats), ncol = 8)
  dat.subset <- dat.all.prime
  z.variable <- "treatment"
  for (j in 1:length(repeats))
  final.mat <- rbind(final.mat, out.mat)
}
final.mat <- as.data.frame(final.mat)
colnames(final.mat) <- c("variable", "subset", "N", "ate", "greater.p.value", "lesser.p.value", "x.sd", "x.mean")
# For the final table.
final.mat.prime = final.mat
```

## Table 1

I succesfully replicated all elements of table 1.

```{r echo = FALSE, warning=FALSE, message=FALSE}

# Table 1

# Create output
output.vars <- c("numberim", "Remain", "Englishlan")
var.names <- c("Number of immigrants be increased?", "Children of undocumented be allowed to stay?", "English as official language?")
# Main results
# Cumalative results output
final.mat.use <- rbind(final.mat.main, final.mat.prime)
final.mat.use$greater.p.value <- as.numeric(as.character(final.mat.use$greater.p.value))
final.mat.use$lesser.p.value <- as.numeric(as.character(final.mat.use$lesser.p.value))
final.mat.use$ate <- as.numeric(as.character(final.mat.use$ate))
final.mat.use$x.mean <- as.numeric(as.character(final.mat.use$x.mean))
final.mat.use$x.sd <- as.numeric(as.character(final.mat.use$x.sd))
final.mat.use$N <- as.numeric(as.character(final.mat.use$N))
final.mat.use$p.value <- final.mat.use$greater.p.value
final.mat.redact <- final.mat.use[, c("variable", "subset", "ate", "p.value", "x.mean", "x.sd", "N")]
final.mat.redact[, c("ate", "p.value", "x.mean", "x.sd")] <- round(final.mat.redact[, c("ate", "p.value", "x.mean", "x.sd")], 3)
final.mat.redact$ate.new <- paste(final.mat.redact$ate, " (", final.mat.redact$p.value, ")", sep = "")
final.mat.redact$x.mean.new <- paste(final.mat.redact$x.mean, " (", final.mat.redact$x.sd, ")", sep = "")
out.mat.a <- final.mat.redact[final.mat.redact$subset == "all" & final.mat.redact$variable %in% output.vars, ]
out.mat.a <- final.mat.redact[final.mat.redact$subset == "all" & final.mat.redact$variable %in% output.vars, c("ate.new")]
out.mat.c <- final.mat.redact[final.mat.redact$subset == "no.car" & final.mat.redact$variable %in% output.vars, c("ate.new")]
out.mat.x <- final.mat.redact[final.mat.redact$subset == "all" & final.mat.redact$variable %in% output.vars, c("x.mean.new")]
# Add the N row (counts). Included a na.rm = TRUE
# call, which was not there in the original replication code.
Ns <- c(
  "n", max(final.mat.redact$N[final.mat.redact$subset == "all"], na.rm = TRUE),
  max(final.mat.redact$N[final.mat.redact$subset == "no.car"], na.rm = TRUE),
  max(final.mat.redact$N[final.mat.redact$subset == "all"], na.rm = TRUE)
)
# Redo the heading portion of the table.
# h1 <- c("", paste("(", 1:3, ")", sep = ""))
# h2 <- c("", "all respondents", "waits on platform", "all respondents")
# h3 <- c("question", "ATE (p)", "CATE (p)", "T1 levels (sd)")
# hs <- rbind(h1, h2, h3)
# row.names(hs) <- NULL
hs <- c("", "ATE (P)", "CATE (P)", "T1 levels (SD)")
row.names(hs) <- NULL
out.mat <- cbind(out.mat.a, cbind(out.mat.c, out.mat.x))
out.mat <- cbind(var.names, out.mat)
out.mat <- rbind(out.mat, Ns)
out.mat <- rbind(hs, out.mat)


# BELOW WE CONVERT THE TABLE INTO GT FOR OUTPUT

# Convert the output into a dataframe and select the appropriate columns

table1Data <- as.data.frame(out.mat)

# Use colnames function to rename the columns

colnames(table1Data) <- c("Question", "All respondents", "Waits on platform", "All respondents.")

# Use gt to create the table

gt(data = table1Data) %>% 
  
# Add in the title of the table
  
  tab_header(
    title = "Table 1. Experimental Results"
  ) %>% 
  
# Add footnotes at the bottom of the table
  
  tab_footnote(
    footnote = "P values from a one-tailed test against the Null Hypothesis of no effect are in parentheses.",
    locations = cells_data(columns = 2, rows = 1)) %>% 
  tab_footnote(
    footnote = "Each pf the questions allowed responses on a five-point scale ranging from strongly agree to strongly disagree (exact answers were changed to be appropriate to the actual question)",
    locations = cells_data(columns = 1, rows = 2)) %>% 
  
  # Add a source note 
  
  tab_source_note(source_note = 'In the first All respondents" column, ATE represents responses in T2-T1 for the treatment group compared with the control group for the entire experimental sample. Positive values mean a more politically conservative response. In the "Waits on platform" column, CATEs are the Conditional Average Treatment Effects for persons who said they stand on the platform, rather than wait in their cars. In the second "All Respondents" column, T1 levels and SDs for each variable for all respondents. All variables scaled 0')
  


```

## Table 2

I was able to succesfully recreate all values of table 2 except for the *n* values and the values of income. Regarding income, it is possible that the author possibly ammended some of the data after publishing it to dataverse. Regarding *n*, I iterated through possible ways to achieve the n values that the author achieved. By removing NA values, the Control *n* value can be achieved, but I am unsure how the treatment *n* value was achieved.

```{r table2, echo = FALSE, message = FALSE, warning=FALSE, include = FALSE}

# Table 2

# BALANCE CHECK: Check to see whether there are confounding varaibles 
#   relating to which station is being sampled
# xBalance function calculates std mean dif. along each covariate, given
#   covariates, a treatment variable and a stratifying factor (factor which
#   can seperate data into subgroups)
# Report indicates which results we would like to see
# Strata refers to the set of the population which is being sampled. In this 
#   case, it is the list of train stations

out.balance.test <- xBalance(fmla = treatment ~ liberal+republican+obama.disapprove+ride.everyday+voted.2010+romney.voter+Hispanics.x+age+residency.new+hispanic.new+college+income.new+male+white, data = dat.all, report = c("std.diffs","z.scores","adj.means","chisquare.test"), strata = factor(dat.all$station))

# Convert the output into a dataframe and select the appropriate columns

table2Data <- as.data.frame(out.balance.test) %>% 
  select(results.treatment.0.strat, 
         results.treatment.1.strat,
         results.std.diff.strat,
         results.z.strat)

# Use the data table package to turn the row titles into a colunn

setDT(table2Data, keep.rownames = TRUE)[]

# Use colnames function to rename the columns

colnames(table2Data) <- c("Condition", "Control", "Treatment", "Standard difference", "Z score")

# Rename the Condition column to appropriate values

table2Data$Condition <- c("Liberal", 
                         "Republican", 
                         "Obama Disapprove", 
                         "Ride MBTA every day",
                         "Voted 2010",
                         "Romney voter",
                         "Hispanic threat",
                         "Age",
                         "Residency Year",
                         "Hispanic",
                         "College",
                         "Income",
                         "Male",
                         "White")
dat.all %>% 
  select(income.new) %>% 
  summary()


```

```{r table2Out, echo=FALSE}

# Use gt to create the table

gt(data = table2Data) %>% 

# Round the table values to 2 values

  fmt_number(columns = c("Control", 
                         "Treatment", 
                         "Standard difference", 
                         "Z score"), 
             decimals = 2) %>% 
  
# Add in the title of the table
  
  tab_header(
    title = "Table 2. Covariate Balance across treatment conditions"
  ) %>% 
  
# Add footnotes at the bottom of the table
  
  tab_footnote(
    footnote = "Mean response values for pretreatment variables accounting for stratification into train stations. All variables are 0 and 1 variables, except for Hispanic threat, which is a seven-point scale indicating how threatening respondents find Hispanics, recoded 0-1; residency, which is measured in years; and income, which is annual income in dollars.",
    locations = cells_data(columns = 1, rows = 1)) %>%   
  
  tab_footnote(
    footnote = "Difference in standardized units",
    locations = cells_column_labels(
      columns = c("Standard difference")))

# NOTES: I'm not quite sure what the "n" value refers to. I assumed it would refer to
#   which treatment the user gets, however the number of rows does not add up were this
#   to be true

```

## Graphics

I was able to succesfully recreate the graphics.

```{r echo = FALSE, warning = FALSE, message = FALSE, results = 'asis'}

# I borrowed code for the graphic from Gabe who was my partner for the project.

### Graphics
# Graph presets
os = .4
line.os = .015
y.point = .75
ylims = c(0,1.1)
xlims = c(-.35,.35)
points.cex = 4
lab.cex = 1.5
line.lwd = 4.5
axis.cex = 1.25
colors = brewer.pal(3,'Paired')[1:2] # Colors for pairs used in plots below
# Dose graph
# pdf('dose_combined.pdf', width = 6.5, height = 4)
par(mfrow = c(3,1)) 
par(mar = c(5,0,1,0))
par(bty = 'n')
##dose response graph
out.mat = final.mat.dose[,c('variable','subset','ate','quantile.lower','quantile.upper')]
out.mat$ate = as.numeric(as.character(out.mat$ate))
out.mat$quantile.lower = as.numeric(as.character(out.mat$quantile.lower))
out.mat$quantile.upper = as.numeric(as.character(out.mat$quantile.upper))
out.mat.ta = out.mat[out.mat$subset == 'ta'&out.mat$variable %in% output.vars,]
out.mat.tb = out.mat[out.mat$subset == 'tb'&out.mat$variable %in% output.vars,]
for(i in 1:length(var.names)){
	plot(x  = out.mat.ta$ate[i], y = y.point, 
		xlim = xlims,
		ylim = ylims,
		ylab = '',
		xlab = var.names[i],
		yaxt = 'n',
		type = 'n',
		cex.lab = lab.cex,
		cex.axis = axis.cex)
	lines(x = c(out.mat.ta$quantile.lower[i],out.mat.ta$ate[i]-line.os), 
			y = c(y.point,y.point),
			lty = 1,
			col = colors[1],
			lwd = line.lwd)
	lines(x = c(out.mat.ta$ate[i]+line.os,out.mat.ta$quantile.upper[i]), 
			y = c(y.point,y.point),
			lty = 1,
			col = colors[1],
			lwd = line.lwd)
	lines(x = c(out.mat.tb$quantile.lower[i],out.mat.tb$ate[i]-line.os), 
			y = c(y.point-os,y.point-os),
			lty = 1,
			col = colors[2],
			lwd = line.lwd)
	lines(x = c(out.mat.tb$ate[i]+line.os,out.mat.tb$quantile.upper[i]), 
			y = c(y.point-os,y.point-os),
			lty = 1,
			col = colors[2],
			lwd = line.lwd)
	points(x  = out.mat.ta$ate[i], y = y.point,
		pch = 19,
		cex = points.cex,
		col = colors[1])
	points(x  = out.mat.tb$ate[i], y = y.point - os,
		pch = 1,
		cex = points.cex,
		col = colors[2])
			}
# dev.off()
```


```{r table3, echo = FALSE}

# Could not find data for table 3.

```